\addcontentsline{toc}{chapter}{Acknowledgement}
\setlength{\headsep}{0.4in}
\vspace*{5cm}
\begin{center}

{\bf \LARGE Acknowledgement}

\end{center}

{\noindent \rule{\linewidth}{1mm}} \vspace{0.25in}

\par
Achievements in life are always obtained through some key ingredients added into the recipe which is your work. A spoon of guidance, a touch of inspiration, a squeeze of determination and heaps of blessings are the most crucial among them. This work would not have been possible without the constant support and motivation given to me by my teachers and family.

Hence, I take this opportunity to express gratitude to my guide and mentor, \textbf{Umakanta Majhi}, Assistant Professor, Department of Computer Science and Engineering, National Institute of Technology, Silchar for his expert guidance, innovative suggestions, constant encouragement and patience with which he handled me and the project.His calm minded approach to the project instilled the confidence within me and taught me to embrace the challenges that were ahead.

I am forever grateful to \textbf{Dr. Samir Kumar Borgohain}, Head of the Department, Department of Computer Science and Engineering for his encouragement and considerations throughout my research work. His constant support has been invaluable to me in the pursuit of my research work.

Finally, I express my gratitude to my beloved parents, family and friends who directly or indirectly extended help and prayers to make this thesis successful. 


\vspace{1.5cm}

\begin{flushright}

\textbf{Gautam Jee}

Reg. No- 18-2-5-107
\end{flushright}
\pagebreak
